Centers and centralizers of higher enveloping algebras of Lie algebras

### 2020-09-09 draft.tex
revised AKSZ stuff

\begin{prp}
\label{prp:pair}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ and a quasi-isomorphism of factorization sc-pairs
\[
\bigg( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \bigg) \xto{\simeq} \bigg({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg) \bigg).
\]

In fact, $\bC_n(\fg)$ is a constructible $\PP_0$-factorization algebra and this quasi-isomorphism is compatible with Poisson structures.
\end{prp}

@@

\begin{lmm}
$\bC_n(\fg)$ has the structure of a constructible $\PP_0$-factorization algebra on $M \times \RR_{\geq 0}$. 
\end{lmm}

@@

For any Lie algebra $\fg$, there is a topological field theory defined in any dimension known as {\em topological BF theory}.
Suppose $N$ is an $(n+1)$-dimensional manifold, which for now we assume has no boundary $\partial N = \emptyset$. 
When $N$ is compact, the classical moduli space underlying this topological field theory can be described as the following mapping space 
\begin{equation} \label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G)
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where $G$ is a Lie group whose Lie algebra is $\fg$. 
Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, the AKSZ construction equips the mapping space with a $(-1)$-shifted symplectic structure. 
Classically, on manifolds without boundary, this produce describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.

Now, suppose $N$ has non-empty boundary $\partial N \ne 0$.
Then, (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
However, the AKSZ construction equips 
\[
{\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
\]
with a $0$-shifted symplectic structure. 
Moreover, the restriction map 
\[
{\rm Map}(N_{\rm dR} , {\rm T}^* [n] {\rm B} G) \to {\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
\]
is a Lagrangian morphism. 
\owen{Somewhere say that $N$ and $\partial N$ are still compact here.}
%Perturbatively, this mapping stack represents the restriction of the fields to the boundary.

For BF theory, this $0$-shifted symplectic manifold admits another natural Lagrangian. 
In terms of mapping stacks, it is given by considering maps from $\partial N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
\[
{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e [n] {\rm B}G) .
\]
Then, by higher abstract nonsense \brian{reference} the fiber product
\[
\begin{tikzcd}
X \ar[r] \ar[d] & {\rm Map} (N , {\rm T}^* [n] {\rm B} G) \ar[d] \\
{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e  [n] {\rm B}G) \ar[r] & {\rm Map}(\partial N_{\rm dR} , {\rm T}^*[n]  {\rm B}G)
\end{tikzcd}
\]
is equipped with a $(-1)$-shifted symplectic structure. 
Heuristically, the classical observables are given by functions on the $(-1)$-shifted symplectic space $X$.
\owen{I'm not sure it's a heuristic. I think we could say that we interpret functions on $X$ as the classical observables for the classical field theory with this boundary condition.}

@@

Perturbative BF theory is the formal moduli space is defined by the formal neighborhood of a point in the derived mapping space (\ref{stack1}). 
For simplicity, we will work near the trivial $G$-bundle. 
Here, the formal moduli space is described in terms of the following dg Lie algebra 
\begin{equation}\label{eqn:fields}
\cL = \Omega^{\bu} (N) \otimes \fg \ltimes \Omega^{\bu} (N) \otimes \fg^* [n-3] .
\end{equation}
We denote elements of this dg Lie algebra by pairs $(A,B)$.

The classical {\em fields} of the theory are given by shifting the dg Lie algebra down by one $\cL[1]$. 
One can read off the $(-1)$-symplectic structure on the fields simply by $\int A \wedge B$.

Perturbatively, the classical moduli space is the space of Maurer--Cartan elements of this dg Lie algebra.
These are pairs $(A,B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
\begin{align*}
\d A + \frac12 [A,A] & = 0 \\
\d B + [A,B] & = 0 .
\end{align*}

We remark that we are free to replace $\fg$ by an arbitrary $L_\infty$ algebra, which we will do so for the remainder of this section. 
It is clear that the $L_\infty$ algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$ algebras. 
In the setup of \cite{CG2}, the factorization algebra of classical observables is the Chevalley--Eilenberg cochains $\clies (\cL)$.   
The $\PP_0$-structure is induced from the explicit $(-1)$-symplectic pairing $\int A \wedge B$ at the level of the fields.

So far, we have provided a description of perturbative BF theory on manifolds without boundary. 
More recently, in \cite{ButsonYoo} and \cite{Eugene}, it is shown how to run the perturbative BV formalism on manifolds with boundary which we follow in the definition below.

%Let $N$ be such a manifold with boundary $\partial N \ne \emptyset$ and let $\cE$ denote the space of fields, typically given as the space of sections of a finite rank vector bundle on $N$. 
%The definition of a classical BV theory on $N$ amounts to prescribing the following data:
%\begin{itemize}
%\item[(1)]
%an ordinary classical BV theory on the interior $N \setminus \partial N$ whose space of fields is $\cE|_{N \setminus \partial N}$;
%\item[(2)] 
%a compatible $0$-shifted symplectic structure on $\cE|_{\partial N}$ equipped with a Lagrangian subspace $\cL \subset \cE|_{\partial N}$.
%This is called a {\em boundary condition}.
%\end{itemize}
%From this data at the level of fields, one obtains a constructible $\PP_0$-factorization algebra on the manifold with boundary $N$ at the level of the observables.

@@

>>>>

\begin{prp}
\label{prp:pair}
Let $M$ be a smooth $n$-dimensional manifold and $\fg$ a Lie algebra. 
There is a constructible commutative factorization algebra ${\bf C}_n (\fg)$
%\begin{equation}\label{eqn:graded}
%\left({\bf Bulk}_n (\fg) \; , \; {\rm Gr} \; \bU_n(\fg) \right)
%\end{equation}
on $M \times \RR_{\geq 0}$ and a quasi-isomorphism of factorization sc-pairs
\[
\bigg( {\bf C}_n (\fg)^\circ \; , \; {\bf C}_n (\fg)^\partial \bigg) \xto{\simeq} \bigg({\rm Gr} \; \bZ_n(\fg), {\rm Gr} \; \bU_n(\fg) \bigg).
\]
In fact, $\bC_n(\fg)$ is a constructible $\PP_0$-factorization algebra and this quasi-isomorphism is compatible with Poisson structures.
\end{prp}

@@

\begin{lmm}
$\bC_n(\fg)$ admits the structure of a constructible $\PP_0$-factorization algebra on~$M \times \RR_{\geq 0}$. 
\end{lmm}

@@

For any Lie group $G$, there is a gauge theory defined in any dimension known as {\em topological BF theory}.
Let the ``spacetime'' be an $(n+1)$-dimensional manifold $N$, 
which for now we assume has no boundary $\partial N = \emptyset$. 
As a field theory, there is a system of PDE known as the ``solutions to the equations of motion.''
When $N$ is compact, the moduli space of solutions to these equations of motion for topological BF theory can be described as the mapping space 
\begin{equation} 
\label{stack1}
{\rm Map}(N_{\rm dR} ,  {\rm T}^*[n] {\rm B} G),
\end{equation}
where $N_{\rm dR}$ denotes the de Rham stack of $N$ and where ${\rm B}G$ is the classifying stack of $G$.
Via the canonical $n$-shifted symplectic structure on ${\rm T}^* [n] {\rm B} G$, 
the AKSZ construction equips this mapping space with a $(-1)$-shifted symplectic structure. 
On manifolds without boundary, this procedure describes topological BF theory in the Batalin--Vilkovisky formalism~\cite{BV}.

Now, suppose that our compact manifold $N$ has non-empty boundary $\partial N \ne 0$.
Then (\ref{stack1}) no longer admits a $(-1)$-shifted symplectic structure. 
In this case, the AKSZ construction equips 
\[
{\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
\]
with a $0$-shifted symplectic structure. 
Moreover, the map that restricts a map from all of $N$ to its boundary
\[
{\rm Map}(N_{\rm dR} , {\rm T}^* [n] {\rm B} G) \to {\rm Map}(\partial N_{\rm dR} , {\rm T}^* [n] {\rm B} G)
\]
is a Lagrangian morphism.

For topological BF theory, this $0$-shifted symplectic manifold admits another natural Lagrangian ``subspace.'' 
In terms of mapping stacks, it is given by maps from $\partial N_{\rm dR}$ into the $n$-shifted conormal bundle of ${\rm B} G$:
\[
{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e [n] {\rm B}G) .
\]
The fiber product
\[
\begin{tikzcd}
X \ar[r] \ar[d] & {\rm Map} (N , {\rm T}^* [n] {\rm B} G) \ar[d] \\
{\rm Map}(\partial N_{\rm dR} , {\rm N}^*_e  [n] {\rm B}G) \ar[r] & {\rm Map}(\partial N_{\rm dR} , {\rm T}^*[n]  {\rm B}G)
\end{tikzcd}
\]
is then equipped with a $(-1)$-shifted symplectic structure. 
From the point of view of classical physics, 
we view the algebra of functions $\cO_X$ on $X$ as the {\em classical observables} of topological BF theory with these boundary conditions.

\owen{Brian: please edit this paragraph.}
Although we have started here with a Lie group $G$, 
one can replace $T^*[n] {\rm B}G$ with {\em any} $n$-shifted symplectic derived stack.
Such AKSZ theories encompass examples of interest in physics (e.g., the A- and B-models or Rozansky-Witten theories).
Of particular interest to us here are the shifted cotangent spaces~$T^*[n] X$.

We now turn to relating these ideas to the constructions of this paper.

@@

Perturbative BF theory for the group $G$ is the formal moduli space is defined by the formal neighborhood of a point in a derived mapping space such as (\ref{stack1}). 
For simplicity, consider working around the trivial $G$-bundle. 
Here, the formal moduli space is described in terms of the following dg Lie algebra 
\begin{equation}\label{eqn:fields}
\cL = \Omega^{\bu} (N) \otimes \fg \ltimes \Omega^{\bu} (N) \otimes \fg^* [n-3] .
\end{equation}
We denote elements of this dg Lie algebra by pairs~$(A,B)$.

\begin{rmk}
In the physics literature, one does not work with the $L_\infty$ algebra $\fg$ arising from a formal moduli space,
but the shifted $L_\infty$ algebra $\fg[1]$. 
In physical terminology, the classical {\em fields} here are $A$ and $B$, 
and the $(-1)$-shifted symplectic structure on the fields is~$\int A \wedge B$. 
\end{rmk}

Perturbatively, the classical moduli space is the space of Maurer--Cartan elements of this dg Lie algebra.
These are pairs $(A,B)$ where $A \in \Omega^1 (N) \otimes \fg$ and $B \in \Omega^{n-1} (N) \otimes \fg^*$ satisfying the equations
\begin{align*}
\d A + \frac12 [A,A] & = 0 \\
\d B + [A,B] & = 0 ,
\end{align*}
which ask for a flat $G$-connection $\d + A$ and a flat section $B$ in the coadjoint bundle.

As noted earlier, we could replace ${\rm B}G$ by any (reasonable) derived stack $X$.
In that setting, the ordinary Lie algebra $\fg$ is replaced by the $L_\infty$ algebra describing the formal neighborhood of some point on $X$.
(Or, more generally, the $L_\infty$ algebra describing the formal neighborhood around some point on the whole mapping space.)
Indeed, we might as well view $\fg$ as an arbitrary $L_\infty$ algebra,
which we will do for the remainder of this section.

\begin{rmk}
The $L_\infty$ algebra $\cL$ in (\ref{eqn:fields}) can be enhanced to a sheaf of $L_\infty$ algebras,
and it can be understood as a generalized topological BF theory. 
In the setup of \cite{CG2}, the factorization algebra of classical observables of generalized topological BF theory is given by the Chevalley--Eilenberg cochains $\clies (\cL)$.   
The $\PP_0$-structure is induced from the explicit $(-1)$-symplectic pairing $\int A \wedge B$ at the level of the fields. 
\end{rmk}

So far, we have provided a description of perturbative BF theory on manifolds without boundary. 
More recently, in \cite{ButsonYoo} and \cite{Eugene}, 
it is shown how to extend the perturbative BV formalism to manifolds with boundary, 
which we follow in the definition below.

@@

\owen{$\PP_0$ algebras?}
